An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-17 arxiv/poly-embed.tex
added arxiv fork

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage{neurips_2019}

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro\raf{Jessie?} \\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others? already a bit much...}, these works are mostly concerned with point estimation problems.
Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.

@@

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
\btw{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

@@

\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.  Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.  In contrast, we focus exclusively on non-strictly-convex risks.}

@@

  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
  For any $p\in\simplex$, we have
  \begin{align*}
    \risk{L}(p)
    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}\\
    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)\\
    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
  \end{align*}
  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
  \btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
\end{proof}

\btw{Cut summary for now (Why is this cool?)}

@@

\bo{Removed comments to point to appendix, since that creates more links...}
Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}

% \begin{proposition}
%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
% \end{proposition}
% \begin{proof}
%   \raf{Use Hari's theorems from their section 8.}
% \end{proof}

@@

\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part. This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  [[Is this true?]]}

@@

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}

@@

Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

@@

In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In the full version of the paper\raft{add cite later}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.

@@

\subsection{Inconsistency of top-$k$ losses}
% 7.14.19- proposed version for arXiv
\btw{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}

@@

% \jessie{Not sure if this is too much detail...}
% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.

@@

%In Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.

@@

%% %For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.

%%%% Pre-neurips
%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.  % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
%
%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
%We also saw that it is a general technique that can be used for any finite elicitable property.
%
%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
%\jessie{Add more?}

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
% \subsection*{Acknowledgements}
% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
% Arpit
% Eric Balkanski for a proof of \raf{Lemma on submodularity}
% NSF grant
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\raft{Note for later: should be able to show that the union of trim is the simplex.}
Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

@@

\begin{lemma}
  \label{lem:poly-loss-poly-risk}
  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
  \btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
\end{proof}

@@

\begin{lemma} \label{lemma:distance-loss}
  \raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
\end{lemma}
\begin{proof}
  Fix $p$ and let $U = \Gamma(p)$.
  If $u \in U$, then both sides are zero.
  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.

@@

>>>>

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage[preprint]{neurips_2019}

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro\\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}\\
 Microsoft Research, CU Boulder
}

@@

While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.

@@

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
%\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
%\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
%\btw{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

@@

    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

@@

%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.  Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency.}
%\btw{RF: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.  In contrast, we focus exclusively on non-strictly-convex risks.}

@@

  We compute Bayes risks and apply Proposition~\ref{prop:embed-bayes-risks} to see that $L$ embeds $\ell$.
  For any $p\in\simplex$, we have
  \begin{align*}
    \risk{L}(p)
    &= \inf_{u\in\reals^n} \inprod{p}{C(u)\ones - u}\\
    &= \inf_{u\in\reals^n} C(u) - \inprod{p}{u}\\
    &= -\sup_{u\in\reals^n} \inprod{p}{u} - C(u)\\
    &= -C^*(p) = - (-\risk{\ell}(p))^{**} = \risk{\ell}(p)~.
  \end{align*}
  It remains to show $L(u)_y \geq 0$ for all $u\in\reals^n$, $y\in\Y$.
  Letting $\delta_y\in\simplex$ be the point distribution on outcome $y\in\Y$, we have for all $u\in\reals^n$, $L(u)_y \geq \inf_{u'\in\reals^n} L(u')_y = \risk{L}(\delta_y) = \risk{\ell}(\delta_y) \geq 0$, where the final inequality follows from the nonnegativity of $\ell$.
  %\btw{FUTURE: to get $n-1$, just use the same trick as before and note that the Bayes risk doesn't change.  Should be a couple lines.  (Not needed for NeurIPS since we don't focus on the dimension.)}
\end{proof}

%\btw{Cut summary for now (Why is this cool?)}

@@

%\bo{Removed comments to point to appendix, since that creates more links...}
Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

%\btw{JOURNAL: cool to point out that when $L$ is polyhedral, $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}

% \begin{proposition}
%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. %\jessie{Rephrase?}
% \end{proposition}
% \begin{proof}
%   \raf{Use Hari's theorems from their section 8.}
% \end{proof}

@@

%\btw{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part. This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
%\btw{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  [[Is this true?]]}

@@

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
%\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube.}

@@

Rather than formally define the Lov\'asz hinge, we defer the complete analysis to Appendix~\ref{app:lovasz}, and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

@@

In fact, this example is typical: using our embedding framework, and characterizing when $0\in\reals^2$ is an embedded point, one can show that $L^g$ is consistent if and only if $g_{1,2} = g_1 + g_2$.
Moreover, in the linear case, which corresponds to $g$ being \emph{modular}, the Lov\'asz hinge reduces to weighted Hamming loss, which is trivially consistent from the consistency of hinge loss for 0-1 loss.
In Appendix~\ref{app:lovasz}, we generalize this observation for all $k$: $L^g$ is consistent if and only if $g$ is modular.
In other words, even for $k>2$, the only consistent Lov\'asz hinge is weighted Hamming loss.
These results cast doubt on the effectiveness of the Lov\'asz hinge in practice.

@@

\subsection{Inconsistency of top-$k$ losses}
% 7.14.19- proposed version for arXiv
%\btw{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}

@@

% %\jessie{Not sure if this is too much detail...}
% Since $\prop{\elltop{2}}$ does not refine $\prop{L^2}$, then $L^2$ does not embed $\elltop{2}$.
% For example, we can take distributions $p_1 \in \gamma^{top-2}_{\{1,2\}}$ and $p_2 \in \gamma^{top-2}_{\{1,3\}}$ such that $p_1, p_2 \in \Gamma_{(1,0,0)}$.
% Regardless of $\psi((1,0,0))$, for either $p_1$ or $p_2$, we will observe $\psi((1,0,0)) \not \in \argmin_u \inprod{p_i}{\elltop{2}(u)}$.
% Thus, we see that $L^2$ is not a consistent surrogate for $\elltop{2}$.

@@

%In Lemma~\ref{lem:top-k-optimal-corners}%\jessiet{in the Appendix... remove ref for camera ready version}, we show that the set $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$, meaning for all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.

@@

%% %For any $r$ such that $|r| \geq 2$ %\jessiet{In general, $|r| \geq k+1$}, we know that  $\ell'(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.%\bo{commented stuff for space}
%We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
%While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
%Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.

%%%% Pre-neurips
%This work is part of a broader research program to understand convex surrogates through the lens of property elicitation.  % the relationship between finite losses and convex surrogates, the link functions connecting them, and the properties they elicit.
%We seek a general theory that, given a property, can prescribe when and how to construct convex surrogate losses that elicit it, and specifically, determine the minimum dimension required.
%Even more broadly, one could replace ``convex'' by any notion of ``nice'' surrogate.
%
%This work formalized the \emph{embedding} approach where labels are identified with points in $\reals^d$.
%We saw in Theorems~\ref{thm:poly-embeds-discrete} and~\ref{thm:discrete-loss-poly-embeddable} that this approach is tightly connected to the use of polyhedral (i.e. piecewise linear convex) loss functions.
%We also saw that it is a general technique that can be used for any finite elicitable property.
%
%Moreover, we established the relationship between polyhedral surrogates and \emph{calibrated links} to the discrete losses they embed.
%%\jessie{Add more?}

@@

%\raf{ACKNOWLEDGEMENTS (commented out for submission)}
 \subsection*{Acknowledgements}
 We thank Peter Bartlett for several discussions early on, which led to our 1-dimensional characterization.  %to a proof of %\raf{1-d reduction} among other insights.
 Additionally, we thank Arpit Agarwal for early insights and bringing out attention to the abstain property.
 We thank Eric Balkanski for the insight that led to the proof of Lemma~\ref{lem:bar-f}.
 JF and RF were funded by NSF grant \#1657598.
\newpage
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

%\raft{Note for later: should be able to show that the union of trim is the simplex.}
Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

@@

\begin{lemma}
  \label{lem:poly-loss-poly-risk}
  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
  %\btw{RF: interesting: we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
\end{proof}

@@

\begin{lemma} \label{lemma:distance-loss}
  %\raft{What I changed: linear ftn $\to$ affine; name the cell $U_f$ for $f$; also name set of functions $\F$, normals $V_f$, etc}
  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
\end{lemma}
\begin{proof}
  Fix $p$ and let $U = \Gamma(p)$.
  If $u \in U$, then both sides are zero.
  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.

@@

%\raf{Note for camera-ready and/or journal version: we should at some point beef up the restriction lemma ($L|_\R$) so that it says $L$ embeds $L|_\R$.  To do this, we'll need to relax our definition of discrete loss to allow for redundant reports.  Maybe say a loss is \emph{minimal} if there are no such reports, and use this in the few results that rely on non-redundancy (like the matching Bayes risks result).  Then for sufficient conditions we can talk about embedding without worrying about showing non-redundancy, which seems to be most useful in practice.}

\section{Lov\'asz Hinge}\label{app:lovasz}
